### 2018-08-06 paper/finitecomplete-failures.tex
Improvements suggested by Wen-ling

\begin{lemma}
\label{lemma:extendV}
Let $P$ be a CSP process with normalised transition graph $G(P)$, 
such that all states in $N$ are reachable.
Let $V\subseteq\Sigma^*$ be a finite prefix-closed set of
sequences of events. Suppose that  $G(P)$ reaches $k < |N|$ nodes under $V$, that is,
$|t(\ii n,V)| = k$. Let $V.\Sigma$ denote the set of all sequences from $V$, extended by an event of $\Sigma$.
Then $G(P)$ reaches at least $(k+1)$ nodes under $V\cup V.\Sigma$.
\end{lemma}
\begin{proof}
Suppose that $n'\in (N - t(\ii n,V))$.  Since all nodes in $N$ are reachable, there exists
a trace $s$ such that $G(P)/s = n'$. Decompose $s = s_1.e.s_2$ with $s_i\in\Sigma^*, e\in\Sigma$, such that $G(P)/s_1 \in t(\ii n,V)$ and $G(P)/s_1.e \not\in t(\ii n,V)$. Such a decomposition always exists, because $V$ is prefix-closed and therefore contains the empty trace $\varepsilon$. Note, however, that it is not necessarily the case that $s_1\in V$.

Since $G(P)$ reaches $G(P)/s_1$ under $V$, there exists a trace $u\in V$ such that
$\ol n = G(P)/u = G(P)/s_1$. Since $s = s_1.e.s_2$ is a trace of $P$ and $n = G(P)/s_1$,
$(\ol u,e)$ is in the domain of $t$, therefore,  
$n = G(P)/u.e = G(P)/s_1.e \not\in t(\ii n,V)$ is a well-defined node
of $N$ which is not contained in $t(\ii n,V)$. Since $u.e\in V\cup V.\Sigma$,
$G(P)$ reaches at least the additional node $n$ under $V\cup V.\Sigma$. This completes the proof.
\xbox
\end{proof}

@@

For a given reference process $P$ and for each $n\ge 0$, 
we define a CSP test process as follows. 
\begin{eqnarray}
U_F(n) & = & U_F(n,\varepsilon)
\\
U_F(n,s) & = & \big( e:(\Sigma - [P/s]^0) \then \dag\then \Skip \big)
\label{eq:ufa}
\\ & & \extchoice \nonumber
\\ & & ([P/s]^0 = \varnothing)    \&   \big( \omega \then \Skip \big)
\label{eq:ufb}
\\ & & \extchoice \nonumber
\\ & & (\#s < n) \& \big( e:[P/s]^0 \then U_F(n,s.e) \big)
\label{eq:ufc}
\\ & & \extchoice \nonumber
\\ & & (\#s = n) \& \big( \sqcap_{H\in\text{MINHIT}(P/s)} ( e:H \then \omega \then\Skip   )  \big)
\label{eq:ufd}
\end{eqnarray}

A test is performed by running $U_F(n)$ concurrently with any SUT process $Q$
that operates on the same alphabet as $P$, synchronising over
alphabet $\Sigma$. Therefore, a test execution is any trace of the concurrent process
\[
Q\parallel[\Sigma] U_F(n).
\]
It is assumed that the events $\dag$ and $\omega$ denoting FAIL and PASS of the test execution, respectively, are events outside $\Sigma$.
Since we assume that $Q$ is free of livelocks, it is guaranteed that each test execution terminates after some $s\in\trc(P)$ with length $(n+1)$ at the latest. 
The test is \emph{passed} by the SUT (we write $Q\ \pass\ U(n)$) if and only if {\it every} execution of $Q\parallel[\Sigma] U_F(n)$ terminates with PASS event $\omega$. This can also be  expressed by means of a trace equivalence relation:
\[
Q\ \pass\ U(n) \equiv  (Q\parallel[\Sigma] U_F(n)) \hide \Sigma =_T (\omega\then\Skip)
\]
This type of pass relation is often called \emph{must test}, because every test execution must end with the PASS event $\omega$ \cite{Hennessy:1988:ATP:50497}.

Intuitively speaking, $U_F(n)$ is able to perform any trace $s$ of $P$, 
up to a length of $n$. If, after having already run through $s\in\trc(P)$ with $\#s < n$,
an event is accepted by the SUT which is outside the initials of $P/s$, the test 
immediately terminates with FAIL-event $\dag$. This is handled by the first operand of the
external choice in sub-process $U(n,s)$.

If $P/s$ is the STOP-process, this is revealed by its initials being empty. In this case, the test may terminate 
successfully (second operand of the external choice in $U(n,s)$). Note that at the same time, any (now illegal) event of the alphabet is also accepted by the test.
Therefore,
if the SUT would still accept an event in a state where $P/s$ is supposed to have stopped, there exists a test execution which terminates with FAIL by choosing the first
operand of the external choice.

If the length of $s$ is still less than $n$, the test accepts any event from the initials
$[P/s]^0$ and continues recursively as sub-process $U(n,s.e)$ (third operand of the external choice). A test of this type is called \emph{adaptive}, because it accepts any legal behaviour of the SUT and adapts its consecutive behaviour to the event selected by the SUT.

After having  run successfully 
through a trace of length $n$, the test changes its behaviour:
instead of offering {\it all} legal events from $[P/s]^0$ to the SUT, 
it nondeterministically chooses 
a minimal hitting set of $\minaccs(P/s)$ and only offers the events contained in this set.
If the SUT refuses to engage into any of these events, this reveals a violation of the
failures refinement: according to Lemma~\ref{lemma:hseta}, a conforming SUT should accept
at least one event of each minimal hitting set in $\text{MINHIT}(P/s)$. Therefore, the test
only terminates with success $\omega$, if such an event is accepted by the SUT.

@@

\begin{theorem}
Let $P$ be a divergence-free CSP process over alphabet $\Sigma$ 
whose normalised transition graph $G(P)$ has $n$ states. Define fault domain ${\cal D}$ as
the set of all divergence-free CSP processes over alphabet $\Sigma$, whose transition graph
has at most $m$ states with $m \ge n$. 
Then the test suite 
\[
\TS_F = \{ U_F(k)~|~0 \le k \le nm  \}
\]
is complete with respect to ${\cal F} = (P,\lessdet_F,{\cal D})$.
\end{theorem}
\begin{proof}
To prove soundness of $\TS_F$, suppose that $Q\in{\cal D} \wedge P\lessdet_F Q$. Then
$\trc(Q)\subseteq \trc(P)$, and Lemma~\ref{lemma:hseta} implies that 
for all traces $s$ of $Q$, every $H\in\text{MINHIT}(P/s)$ is a 
    hitting set for $\minaccs(Q/s)$. As a consequence, when running in parallel
with $Q$, any adaptive test $U_F(n)$ will always enter the branches 
(\ref{eq:ufb}), (\ref{eq:ufc}),  or (\ref{eq:ufd}) of the external choice construction
for $U_F(n,s)$. Branch (\ref{eq:ufb}) always leads to a PASS verdict, branch (\ref{eq:ufc})
always to test continuation without a verdict. For the last branch, we note that 
any selected minimal hitting set $H\in\text{MINHIT}(P/s)$ has a non-empty intersection with
each of the minimal acceptances of $Q/s$. As a consequence, $Q/s$ will never block when offered events from $H$, and the test terminates with PASS event $\omega$. Note that this argument requires that $Q$ is free of livelocks, because otherwise the PASS-events might not become visible, due to unbounded sequences of hidden events performed by $Q$. Note further, that this proof did not refer in any way to the size of $Q$'s normalised transition graph, so the test suite is sound for {\it all} non-divergent CSP process refining $P$.

To prove exhaustiveness, consider a process $Q\in{\cal D}$ with $P\not\lessdet_F Q$. This non-conformance can be caused in two possible ways.
\begin{enumerate}
\item $\trc(Q)\not\subseteq \trc(P)$
\item There exists a joint trace $s\in\trc(Q)\cap\trc(P)$ and a minimal acceptance $A_Q$
of $\minaccs(Q/s)$, such that 
(see Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb})).
\[
\forall A_P\in\minaccs(P/s): A_P\not\subseteq A_Q,
\] 
\end{enumerate}
It has to be shown for each of the two possibilities that at least one test execution of some $(Q\parallel[\Sigma] U(k))$ with $k\le nm$ ends with the FAIL event $\dag$.
\xbox
\end{proof}

>>>>

\begin{lemma}
\label{lemma:extendV}
Let $P$ be a CSP process with normalised transition graph $G(P)$, 
such that all states in $N$ are reachable.
Let $V\subseteq\Sigma^*$ be a finite prefix-closed set of
sequences of events. Suppose that  $G(P)$ reaches $k < |N|$ nodes under $V$, that is,
$|t(\ii n,V)| = k$. Let $V.\Sigma$ denote the set of all sequences from $V$, 
extended by any event of $\Sigma$.
Then $G(P)$ reaches at least $(k+1)$ nodes under $V\cup V.\Sigma$.
\end{lemma}
\begin{proof}
Suppose that $n'\in (N - t(\ii n,V))$.  Since all nodes in $N$ are reachable, there exists
a trace $s$ such that $G(P)/s = n'$. Decompose $s = s_1.e.s_2$ with $s_i\in\Sigma^*, e\in\Sigma$, such that $G(P)/s_1 \in t(\ii n,V)$ and $G(P)/s_1.e \not\in t(\ii n,V)$. Such a decomposition always exists, because $V$ is prefix-closed and therefore contains the empty trace $\varepsilon$. Note, however, that it is not necessarily the case that $s_1\in V$.

Since $G(P)$ reaches $G(P)/s_1$ under $V$, there exists a trace $u\in V$ such that
$\ol n = G(P)/u = G(P)/s_1$. Since $s = s_1.e.s_2$ is a trace of $P$ and 
$\ol n = G(P)/s_1$,
$(\ol n,e)$ is in the domain of $t$. Therefore,  
$n = G(P)/u.e = G(P)/s_1.e \not\in t(\ii n,V)$ is a well-defined node
of $N$ which is not contained in $t(\ii n,V)$. Since $u.e\in V\cup V.\Sigma$,
$G(P)$ reaches at least the additional node $n$ under $V\cup V.\Sigma$. This completes the proof.
\xbox
\end{proof}

@@

For a given reference process $P$ and for each integer $p\ge 0$, 
we define a CSP test process as follows. 
\begin{eqnarray}
U_F(p) & = & U_F(p,\varepsilon)
\\
U_F(p,s) & = & \big( e:(\Sigma - [P/s]^0) \then \efail\then \Stop \big)
\label{eq:ufa}
\\ & & \extchoice \nonumber
\\ & & ([P/s]^0 = \varnothing)    \&   \big( \epass \then \Stop \big)
\label{eq:ufb}
\\ & & \extchoice \nonumber
\\ & & (\#s < p) \& \big( e:[P/s]^0 \then U_F(p,s.e) \big)
\label{eq:ufc}
\\ & & \extchoice \nonumber
\\ & & (\#s = p) \& \big( \sqcap_{H\in\text{minHit}(P/s)} ( e:H \then \epass \then\Stop   )  \big)
\label{eq:ufd}
\end{eqnarray}

A test is performed by running $U_F(p)$ concurrently with any SUT process $Q$
that operates on the same alphabet as $P$, synchronising over
alphabet $\Sigma$. Therefore, a test execution is any trace of the concurrent process
\[
Q\parallel[\Sigma] U_F(p).
\]
It is assumed that the events $\efail$ and $\epass$ denoting FAIL and PASS of the test execution, respectively, are events outside $\Sigma$.
Since we assume that $Q$ is free of livelocks, it is guaranteed that each test execution terminates after some $s\in\trc(P)$ with length $(p+1)$ at the latest. 
The test is \emph{passed} by the SUT (we write $Q\ \pass\ U_F(p)$) if and only if {\it every} execution of $Q\parallel[\Sigma] U_F(p)$ terminates with PASS event $\epass$. This can also be  expressed by means of a failures refinement relation:
\[
Q\ \pass\ U_F(p) \equiv (\epass\then\Stop) \lessdet_F (Q\parallel[\Sigma] U_F(p)) \hide \Sigma  
\]
This type of pass relation is often called \emph{must test}, because every test execution must end with the $\epass$-event \cite{Hennessy:1988:ATP:50497}. Note that it
is necessary to use the failures refinement relation in this condition, and not the trace refinement relation: process $(Q\parallel[\Sigma] U_F(p)) \hide \Sigma$ may have  the same visible traces $\varepsilon, \epass$ as the ``Test Passed Process'' $(\epass\then\Stop)$. However,
the former may nondeterministically refuse $\epass$, due to a deadlock occurring when
a faulty SUT process executes concurrently with $U_F(p,s)$ executing branch (\ref{eq:ufd}),
because $\#s = p$. This is explained further in the next paragraphs.

Intuitively speaking, $U_F(p)$ is able to perform any trace $s$ of $P$, 
up to a length of $p$. 
If, after having already run through $s\in\trc(P)$ with $\#s < p$,
an event is accepted by the SUT which is outside the initials of $P/s$, the test 
immediately terminates with FAIL-event $\efail$. This is handled by the first operand of the
external choice in sub-process $U_F(p,s)$.

If $P/s$ is the STOP-process, this is revealed by its initials being empty. In this case, the test may terminate 
successfully (second operand of the external choice in $UF(p,s)$). Note that at the same time, any (now illegal) event of the alphabet is also accepted by the test.
Therefore,
if the SUT would still accept an event in a state where $P/s$ is supposed to have stopped, there exists a test execution which terminates with FAIL by choosing the first
operand of the external choice.

If the length of $s$ is still less than $p$, the test accepts any event from the initials
$[P/s]^0$ and continues recursively as sub-process $U(p,s.e)$ (third operand of the external choice). A test of this type is called \emph{adaptive}, because it accepts any legal behaviour of the SUT and adapts its consecutive behaviour to the event selected by the SUT.

After having  run successfully 
through a trace of length $p$, the test changes its behaviour:
instead of offering {\it all} legal events from $[P/s]^0$ to the SUT, 
it nondeterministically chooses 
a minimal hitting set of $\minaccs(P/s)$ and only offers the events contained in this set.
If the SUT refuses to engage into any of these events, this reveals a violation of the
failures refinement: according to Lemma~\ref{lemma:hseta}, a conforming SUT should accept
at least one event of each minimal hitting set in $\text{minHit}(P/s)$. Therefore, the test
only terminates with success $\epass$, if such an event is accepted by the SUT.

@@

\begin{theorem}
Let $P$ be a divergence-free CSP process over alphabet $\Sigma$ 
whose normalised transition graph $G(P)$ has $p$ states. Define fault domain ${\cal D}$ as
the set of all divergence-free CSP processes over alphabet $\Sigma$, whose transition graph
has at most $q$ states with $q \ge p$. 
Then the test suite 
\[
\TS_F = \{ U_F(k)~|~0 \le k < pq  \}
\]
is complete with respect to ${\cal F} = (P,\lessdet_F,{\cal D})$.
\end{theorem}
\begin{proof}
To prove soundness of $\TS_F$, suppose that $Q\in{\cal D} \wedge P\lessdet_F Q$. Then
$\trc(Q)\subseteq \trc(P)$, and Lemma~\ref{lemma:hseta} implies that 
for all traces $s$ of $Q$, every $H\in\text{minHit}(P/s)$ is a 
    hitting set for $\minaccs(Q/s)$. As a consequence, when running in parallel
with $Q$, any adaptive test $U_F(p)$ will always enter the branches 
(\ref{eq:ufb}), (\ref{eq:ufc}),  or (\ref{eq:ufd}) of the external choice construction
for $U_F(p,s)$. Branch (\ref{eq:ufb}) always leads to a PASS verdict, branch (\ref{eq:ufc})
always to test continuation without a verdict. For the last branch, we note that 
any selected minimal hitting set $H\in\text{minHit}(P/s)$ has a non-empty intersection with
each of the minimal acceptances of $Q/s$. As a consequence, $Q/s$ will never block when offered events from $H$, and the test terminates with PASS event $\epass$. Note that this argument requires that $Q$ is free of livelocks, because otherwise the PASS-events might not become visible, due to unbounded sequences of hidden events performed by $Q$. Note further, that this proof did not refer in any way to the size of $Q$'s normalised transition graph, so the test suite is sound for {\it all} non-divergent CSP process refining $P$.

To prove exhaustiveness, consider a process $Q\in{\cal D}$ with $P\not\lessdet_F Q$. This non-conformance can be caused in two possible ways.
\begin{description}
\item[Case~1] $\trc(Q)\not\subseteq \trc(P)$
\item[Case~2] There exists a joint trace $s\in\trc(Q)\cap\trc(P)$ and a minimal acceptance $A_Q$
of $\minaccs(Q/s)$, such that 
(see Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb})).
\begin{equation}
\label{eq:accsnotcontained}
\forall A_P\in\minaccs(P/s): A_P\not\subseteq A_Q,
\end{equation} 
\end{description}
It has to be shown for each of the two possibilities that at least one test execution of some $(Q\parallel[\Sigma] U(k))$ with $k < pq$ ends with the FAIL event $\efail$.

For the first case, consider a  trace $s.e\in\trc(Q)$ such that $s\in\trc(P)$, but 
$s.e\not\in\trc(P)$. Then $s$ is also a trace of the product graph $G = G(P)\times G(Q)$ defined in Section~\ref{sec:ntg}. From the construction of $G$ described there, we know that $G$ has at most $pq$ reachable states, because $G(P)$ has $p$ states, and $G(Q)$ has at most $q$ states. Suppose that $G/s = (n_P,n_Q)$. Applying Lemma~\ref{lemma:extendV} implies that this state can be reached by a trace $u\in\trc(G)$ of length $\#u < pq$. Now the construction of the transition function of $G$ implies that $u$ is also a trace of $P$ and $Q$. Since test $U_F(pq-1)$ accepts all traces of $P$ up to length $pq$, $u$ is also a trace of this test, and, by construction, $U_F(pq-1)/u = U_F(pq-1,u)$. Since $s.e\not\in\trc(P)$,
$e$ is an element of $\Sigma-[P/u]^0$. Therefore, in at least one execution, $U_F(pq-1,u)$ executes its first branch (\ref{eq:ufa}) with this event $e$, so that the test fails with event $\efail$. Again, the assumption of non-divergence of Q is needed for this conclusion.

For the Case~2, we note that trace $s$ is again a trace of the product graph $G$. Therefore, $G/s$ can again be reached by a trace $u\in\trc(Q)\cap\trc(P)$ of maximal length
$\#u < pq$. Consider test $U_F(\# u)$ which satisfies $U_F(\# u)/u = U_F(\#u,u)$, because
it always performs branch (\ref{eq:ufc}) until the trace $u$ has been completely processed. $U_F(\#u,u)$
  may execute branches (\ref{eq:ufa}) or (\ref{eq:ufd}) only: 
Assumption (\ref{eq:accsnotcontained}) in Case~2 implies that $P/s$ has at least one non-empty minimal acceptance, so the guard condition $([P/s]^0 = \varnothing)$ of branch
 (\ref{eq:ufb}) evaluates to $\isf$ for $U_F(\#u,u)$. Moreover, 
 the guard condition $(\#s < p)$
for branch (\ref{eq:ufc}) evaluates to $\isf$ for $U_F(\#u,u)$, too. 
If branch (\ref{eq:ufa}) is executed, the test always fails. If branch (\ref{eq:ufd})
is executed, the test fails for the execution where a minimal hitting set 
$H\in\text{minHit}(P/u)$ is chosen by $U_F(\#u,u)$ which has an empty intersection
with the minimal acceptance $A_Q$ from condition (\ref{eq:accsnotcontained}). The existence of such an $H$ is guaranteed because of Lemma~\ref{lemma:hseta}. As a consequence, there exists 
a test execution   where $Q/u$ selects acceptance $A_Q$ and  $U_F(\#u,u)$ 
selects $H$. This execution deadlocks in 
process state $(Q\parallel[\Sigma]U_F(\# u))/u$, so it cannot 
produce the pass event $\epass$; this  means that the test fails. This concludes the proof.
\xbox
\end{proof}

### 2018-08-06 paper/preliminaries.tex
Improvements suggested by Wen-ling

\begin{example}{ex:a}
Consider the CSP process $P$ defined below, and that the set of events
$\Sigma$ is $\{a,b,c\}$.
\begin{eqnarray*}
P & = & a \then (Q\intchoice R)
\\
Q & = & a \then P \extchoice c \then P
\\
R & = & b \then P \extchoice c \then R
\end{eqnarray*}
Its transition graph $G(P)$ is shown in Fig.~\ref{fig:tga}. Process state
$P/\langle\rangle$ is represented there as Node\_0, with $\{ b,c\}$ as the
only maximal refusal, since $a$ can never be refused, and no other events are
accepted. Having engaged into $a$, the transition emanating from Node\_0
leads to Node\_2 representing  the process state $P/a = Q\intchoice R$. The
internal choice operator induces several refusal sets derived from $Q$ and
$R$. Since these processes accept their initial events in external choice,
$Q\intchoice R$ induces two maximal refusal sets $\{b\}$ and
$\{a\}$. Note that event $c$ can never be refused, since it is not a member
of any maximal refusal.

@@

When testing for failures refinement, it will become apparent that the main idea of the underlying test strategy can be based on solving a \emph{hitting set problem}. Given a collection of finite sets $C = \{ A_1,\dots,A_n\}$ that are each subsets of a universe $\Sigma$, a \emph{hitting set} $H\subseteq\Sigma$ is a set satisfying
\begin{equation}
\label{eq:hit}
\forall A\in C: H\cap C \neq\varnothing.
\end{equation}

A \emph{minimal hitting set} is a hitting set which cannot be further reduced without losing 
the characteristinc property (\ref{eq:hit}). The problem of determining minimal hitting sets is known to be NP-hard~\cite{Book1975-BOOKRM}, but we will see below that it reduces 
the effort of testing for failures refinement from a factor of $2^\Sigma$ to a factor that equals the number of minimal hitting sets.

@@

\begin{lemma}
\label{lemma:hseta}
Let $P, Q$ be two finite-state CSP processes satisfying $P\lessdet_T Q$. 
For each $s\in\trc(P)$,
let $\text{MINHIT}(P/s)$ denote the
collection of all minimal hitting sets of $\minaccs(P/s)$. 
Then the following statements are equivalent.
\begin{enumerate}
\item $P\lessdet_F Q$
\item For all $s\in\trc(P)\cap \trc(Q)$ and $H \in  \text{MINHIT}(P/s)$, $H$ is
a (not necessariliy minimal) hitting set of $\minaccs(Q/s)$.
\end{enumerate}
\end{lemma}
\begin{proof}
For showing ``$1 \Rightarrow 2$'', assume that $P\lessdet_F Q$ and suppose that
$s\in\trc(P)\cap \trc(Q)$. Then Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), 
states that 
\[
\forall A_Q\in\minaccs(G(Q)/s):
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\]
Therefore,
$H \in  \text{MINHIT}(P/s)$ not only implies $H\cap A_P\neq\varnothing$ for all minimal
acceptances $A_P$, but also
$H\cap A_Q\neq\varnothing$ for every minimal acceptance $A_Q$, because $A_P\subseteq A_Q$ for at least one $A_P$. As a consequence, each $H \in  \text{MINHIT}(P/s)$ is also a hitting set for $\minaccs(G(Q)/s)$.

To prove ``$2 \Rightarrow 1$'',
assume $P\lessdet_T Q$, but $P\not\lessdet_F Q$. According to Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), there exists $s\in\trc(P)\cap \trc(Q)$ such that 
\[
\exists A_Q\in\minaccs(G(Q)/s): \forall A_P\in\minaccs(G(P)/s): A_P\not\subseteq A_Q 
\qquad (*)
\]
Define 
\[
\overline H = \bigcup\{ A_P \setminus A_Q~|~A_P\in\minaccs(G(P)/s) \}.
\]
Since $A_P \setminus A_Q \neq\varnothing$ for all $A_P$ because of (*), $\overline H$ is a hitting set
of $\minaccs(G(P)/s)$ which has an  empty intersection with $A_Q$. Minimising 
$\overline H$ induces the existence
of a minimal hitting set $H\in \text{MINHIT}(P/s)$ which is {\it not} a hitting set of 
of $\minaccs(G(Q)/s)$. This completes the proof of the lemma.
\xbox
\end{proof}

>>>>

\begin{example}\label{ex:a}
Consider the CSP process $P$ defined below, and that the set of events
$\Sigma$ is $\{a,b,c\}$.
\begin{eqnarray*}
P & = & a \then (Q\intchoice R)
\\
Q & = & a \then P \extchoice c \then P
\\
R & = & b \then P \extchoice c \then R
\end{eqnarray*}
Its transition graph $G(P)$ is shown in Fig.~\ref{fig:tga}. Process state
$P/\langle\rangle$ is represented there as Node\_0, with $\{ b,c\}$ as the
only maximal refusal, since $a$ can never be refused, and no other events are
accepted. Having engaged into $a$, the transition emanating from Node\_0
leads to Node\_2 representing  the process state $P/a = Q\intchoice R$. The
internal choice operator induces several refusal sets derived from $Q$ and
$R$. Since these processes accept their initial events in external choice,
$Q\intchoice R$ induces two maximal refusal sets $\{b\}$ and
$\{a\}$. Note that event $c$ can never be refused, since it is not a member
of any maximal refusal.

@@

When testing for failures refinement, it will become apparent that the main idea of the underlying test strategy can be based on solving a \emph{hitting set problem}. Given a collection of finite sets $C = \{ A_1,\dots,A_n\}$, such that each $A_i$ is a   
subset of a universe $\Sigma$, a \emph{hitting set} $H\subseteq\Sigma$ is a set satisfying
\begin{equation}
\label{eq:hit}
\forall A\in C: H\cap A \neq\varnothing.
\end{equation}

A \emph{minimal hitting set} is a hitting set which cannot be further reduced without losing 
the characteristic property (\ref{eq:hit}). The problem of determining minimal hitting sets is known to be NP-hard~\cite{Book1975-BOOKRM}, but we will see below that it reduces 
the effort of testing for failures refinement from a factor of $2^\Sigma$ to a factor that equals the number of minimal hitting sets.

@@

\begin{lemma}
\label{lemma:hseta}
Let $P, Q$ be two finite-state CSP processes satisfying $P\lessdet_T Q$. 
For each $s\in\trc(P)$,
let $\text{minHit}(P/s)$ denote the
collection of all minimal hitting sets of $\minaccs(P/s)$. 
Then the following statements are equivalent.
\begin{enumerate}
\item $P\lessdet_F Q$
\item For all $s\in\trc(P)\cap \trc(Q)$ and $H \in  \text{minHit}(P/s)$, $H$ is
a (not necessariliy minimal) hitting set of $\minaccs(Q/s)$.
\end{enumerate}
\end{lemma}
\begin{proof}
For showing ``$1 \Rightarrow 2$'', assume that $P\lessdet_F Q$ and suppose that
$s\in\trc(P)\cap \trc(Q)$. Then Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), 
states that 
\[
\forall A_Q\in\minaccs(G(Q)/s):
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\]
Therefore,
$H \in  \text{minHit}(P/s)$ not only implies $H\cap A_P\neq\varnothing$ for all minimal
acceptances $A_P$, but also
$H\cap A_Q\neq\varnothing$ for every minimal acceptance $A_Q$, because $A_P\subseteq A_Q$ for at least one $A_P$. As a consequence, each $H \in  \text{minHit}(P/s)$ is also a hitting set for $\minaccs(G(Q)/s)$.

To prove ``$2 \Rightarrow 1$'',
assume $P\lessdet_T Q$, but $P\not\lessdet_F Q$. According to Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb}), there exists $s\in\trc(P)\cap \trc(Q)$ such that 
\[
\exists A_Q\in\minaccs(G(Q)/s): \forall A_P\in\minaccs(G(P)/s): A_P\not\subseteq A_Q 
\qquad (*)
\]
Let $A$ be such a set $A_Q$ fulfilling (*).
Define 
\[
\overline H = \bigcup\{ A_P \setminus A~|~A_P\in\minaccs(G(P)/s) \}.
\]
Since $A_P \setminus A \neq\varnothing$ for all $A_P$ because of (*), $\overline H$ is a hitting set
of $\minaccs(G(P)/s)$ which has an  empty intersection with $A_Q$. Minimising 
$\overline H$ induces the existence
of a minimal hitting set $H\in \text{minHit}(P/s)$ which is {\it not} a hitting set  
of $\minaccs(G(Q)/s)$, a contradiction to Assumption~2. This completes the proof of the lemma.
\xbox
\end{proof}
